---
title: "PA1_template.Rmd"
author: "Jeremy Berg"
date: "October 12, 2015"
output: html_document
---

This document contains information regarding the Reproducible Research-Peer Assessment 1.

Load the data.
```{r}
##  Read activity.csv file if it exists
if (file.exists("activity.csv")) {
        Activity_df <- read.csv("activity.csv")
        }
```

Calculate the total number of steps taken per day.
```{r}
Steps_per_day <- tapply(Activity_df$steps, Activity_df$date, sum)
##  Convert results into a data frame
Steps_per_day_df <- data.frame(Steps_per_day)
```

Make a histogram of the total number of steps taken per day
```{r}
##  Make a histogram of results using ggplot2
library(ggplot2)
qplot(Steps_per_day_df$Steps_per_day, geom="histogram")
```

Calculate and report the mean and median of the total number of steps per day
```{r}
##  Ignore missing data
  mean_steps <- mean(Steps_per_day_df$Steps_per_day, na.rm = TRUE)
  median_steps <- median(Steps_per_day_df$Steps_per_day, na.rm = TRUE)
##  Report mean and median values
```
  The mean of the total number of steps taken is `r mean_steps`.
  
  The median of the total number of steps taken is `r median_steps`.


